---
title: "Famous People Rating in Spatial, Temporal, and Social Domains"
author:  <h4 style="font-style:normal">Lily Cheng and Shalmali Patil
date: "5/31/2019"
output: html_document
---

<style type="text/css">

h1.title {
  font-size: 31px;
  font-family: "Helvetica", Times, serif;
  color: DarkBrown;
}


</style>

<br>

- The perceived spatial, temporal, and social distance is based on a 1 - 7 Likert scale. 1 means very close. **7 means very far.**
- The magnitude of social distance represents the size of each bubble. **Big bubble means socially far.** Small bubble means socially close. 
- Actual spatial distance is the Euclidean distance between the place the person is famous and the **University of California, Santa Barbara (34.4140° N, 119.8489° W)**. 
- Actual temporal distance is the time from the person's birth date to **May 21, 2018** when participants completed the rating.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(pwr)
library(knitr)
library(kableExtra)
library(plotly)
library(ggrepel)
library(ggplot2)
library(RColorBrewer)

```


```{r, echo=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
mortality <- read.csv("drug_mortality-2.csv")

```

### Figure 1. Perceived Spatial, Temporal, and Social Distance
<br>

#### a. General Tendency


```{r, fig.width= 9, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}
mortality$alive<-as.factor(mortality$alive)
mortality$alive<-factor(mortality$alive, levels=c("Y","N"), labels=c("Alive","Dead"))
mortality$us<-as.factor(mortality$us)
mortality$us<-factor(mortality$us, levels=c(1,2,3), labels=c("California","Domestic","International"))

graph_1 <-  ggplot(mortality, 
         aes(x = temp_code,
             y = temporal_mean, group = 1,
             label = famous_person,
             text = paste("Name: ", famous_person,
                          "<br>Perceived Spatial Distance: ", spatial_mean,
                          "<br>Perceived Temporal Distance: ", temporal_mean,
                          "<br>Perceived Social Distance: ", social_mean,
                          "<br>Frequency: ", frequency)))+ xlab("Famous People") +
             ylab("Perceived Distance")+ labs(title="  ")+
  geom_line(aes(temp_code, spatial_mean,colour = "Spatial"))+
  geom_line(aes(temp_code, social_mean, colour = "Social"))+
  geom_line(aes(colour = "Temporal"))+
  scale_color_manual(values = c('Spatial' = '#377eb8','Social' = '#4daf4a', 'Temporal' = '#e41a1c'))+ 
  geom_text_repel(size = 3)+
  labs(color = 'Distance \n Domain')+
  ggtitle(" ")

#graph_1
ggplotly(graph_1, tooltip = "text")
```

<br>

#### b. Individual Data

```{r, fig.width= 9.5, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}

graph_1 <-  ggplot(mortality, 
         aes(x = spatial_mean,
             y = temporal_mean,
             label = famous_person,
             text = paste("Name: ", famous_person,
                          "<br>Perceived Spatial Distance: ", spatial_mean,
                          "<br>Perceived Temporal Distance: ", temporal_mean,
                          "<br>Perceived Social Distance: ", social_mean,
                          "<br>Frequency: ", frequency)
             ))+ xlab("Perceived Spatial Distance") +
             ylab("Perceived Temporal Distance")+ labs(title="  ")+ 
  geom_point(aes(size = social_mean, color = famous_person), alpha = 0.4)+
  geom_text_repel(size = 3)+
  labs(color = '\n Famous People List \n size = social distance')+
  theme(legend.position = "NA")

#graph_1

ggplotly(graph_1, tooltip = "text")
```

<br>

### Figure 2. Actual Temporal Distance Over Actual Spatial Distance 

<br>

#### a. Metric
```{r, fig.width = 9, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}



graph_3 <-  ggplot(mortality, 
         aes(x = (real_spatial),
             y = (real_temporal2),
             label = frequency,
             text = paste("Name: ", famous_person,
                          "<br>Actual Spatial Distance: ", real_spatial,"miles",
                          "<br>Actual Temporal Distance: ", real_temporal2, "years",
                          "<br>Perceived Social Distance: ", social_mean,
                          "<br>Living Status: ", alive,
                          "<br>Frequency: ", frequency)
             ))+ xlab("Actual Spatial Distance (in miles)") +
             ylab("Actual Temporal Distance (in years)") + labs(title="  ")+
  geom_smooth(se=F, method="lm", color="grey")+
  geom_point(aes(size = social_mean, color = alive), alpha = 0.4)+
  geom_text_repel(size = 3)+
  labs(color = 'size = \n social distance \n \n living \n status ')+
  theme(legend.position = "NA")

# graph_3

ggplotly(graph_3, tooltip = "text")
```

<br>

#### b. Logrithm
```{r, fig.width = 9, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}

graph_4 <-  ggplot(mortality, 
         aes(x = log(real_spatial),
             y = log(real_temporal2),
             label = frequency,
             text = paste("Name: ", famous_person,
                          "<br>Actual Spatial Distance: ", real_spatial,"miles",
                          "<br>Actual Temporal Distance: ", real_temporal2, "years",
                          "<br>Perceived Social Distance: ", social_mean,
                          "<br>Frequency: ", frequency)
             ))+ xlab("Log of Actual Spatial Distance (in miles)") +
             ylab("Log of Actual Temporal Distance (in years)") + labs(title="  ")+
  geom_smooth(se=F, method="lm", color="grey")+
  geom_point(aes(size = social_mean, color = alive), alpha = 0.4)+
  geom_text_repel(size = 4)+
  labs(color = 'size = \n social distance \n \n living \n status ')+
  theme(legend.position = "NA")

# graph_4

ggplotly(graph_4, tooltip = "text")
```
<br>

### Figure 3. Perceived Distance Over Actual Distance 
<br>

#### a. Perceived Temporal Distance Over Actual Temporal Distance 
```{r, fig.width = 9, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}
#mortality$alive<-as.factor(mortality$alive)
#mortality$alive<-factor(mortality$alive, levels=c("Y","N"), labels=c("Alive","Dead"))

graph_4 <-  ggplot(mortality, 
         aes(x = log(real_temporal),
             y = temporal_mean,
             label = famous_person))+
  geom_point()+
  geom_text_repel()

graph_4 <-  ggplot(mortality, 
         aes(x = log(real_temporal),
             y = temporal_mean,
            label = famous_person,
             text = paste("Name: ", famous_person,
                          "<br>Actual Temporal Distance: ", real_temporal2, "years",
                          "<br>Perceived Temporal Distance: ", temporal_mean,
                          "<br>Perceived Social Distance: ", social_mean,
                         "<br>Living Status: ", alive,
                          "<br>Frequency: ", frequency)))+ xlab("Log of Real Temporal Distance (in days)") +
             ylab("Perceived Temporal Distance") + labs(title=" ")+
  geom_smooth(se=F, method="lm", color="grey")+
  geom_point(aes(size = social_mean, color = alive), alpha = 0.4)+
  geom_text_repel(size = 3)+
  theme(legend.position = "NA")+
  labs(color = 'size = \n social distance \n\nliving status ')

# graph_4

ggplotly(graph_4, tooltip = "text")

```
<br>

#### b. Perceived Spatial Distance Over Actual Spatial Distance 

```{r, fig.width = 9, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE}
#mortality$us<-as.factor(mortality$us)
#mortality$us<-factor(mortality$us, levels=c(1,2,3), labels=c("California","Domestic","International"))

graph_5 <-  ggplot(mortality, 
         aes(x = log(real_spatial),
             y = spatial_mean,
             label = famous_person,
             text = paste("Name: ", famous_person,
                          "<br>Actual Temporal Distance: ", real_temporal2, "years",
                          "<br>Perceived Temporal Distance: ", temporal_mean,
                          "<br>Perceived Social Distance: ", social_mean,
                          "<br>Place: ", us,
                          "<br>Frequency: ", frequency))) + xlab("Log of Actual Spatial Distance (in miles)") +
             ylab("Perceived Spatial Distance") +labs(title=" ")+
  geom_smooth(se=F, method="lm", color="grey",alpha=0.1)+
  geom_point(aes(size = social_mean, color = us), alpha = 0.4)+
  geom_text_repel(size = 3)+
  labs(color = 'size = \n social distance \n\n\n place \n category')+
  theme(legend.position = "NA")

# graph_5

ggplotly(graph_5, tooltip = "text")

```




